\documentclass{schedule}

\setAdoptedLongDate{13th of March, 2024}

\begin{document}

\input{titlepage}

\pagenumbering{roman}
\tableofcontents
\newpage

\pagenumbering{arabic}

\section{Introduction}

\subsection{Purpose}
The purpose of this Schedule is to establish a register of positions within the Club and detail the composition of the non-executive committee and their responsibilities.

\subsection{Definitions}
Definitions of terms used in this Schedule are as defined in the Constitution.

\subsection{Precedence of Positions}
Positions are defined \Cref{composition}, in order of precedence.

\subsection{Amendments}
\begin{enumerate}[(1)]
    \item This Schedule may be amended by the Executive by a simple majority vote. This includes the ability to establish new positions, or to remove existing positions, as well as to amend the responsibilities of existing positions.
    \item Any amendments to this Schedule must be consistent with the Constitution and the Clubs Policy of YouX.
\end{enumerate}


\section{Composition}\label{composition}
\begin{enumerate}[(1)]
    \item The executive committee consists of:
          \begin{enumerate}[(a)]
              \item the President; and
              \item the Vice-President; and
              \item the Treasurer; and
              \item the Secretary; and
              \item the Partnerships \& Sponsorships Manager.
          \end{enumerate}
    \item The non-executive committee consists of:
          \begin{enumerate}[(a)]
              \item the Duck Lounge Liaison; and
              \item the Business Manager; and
              \item up to two Partnerships \& Sponsorships Officers; and
              \item the Social Media \& Marketing Manager; and
              \item up to two Graphic Designers; and
              \item up to two Social Media \& Marketing Officers; and
              \item up to two Open Source Officers; and
              \item the Equity Officer; and
              \item the First-Year Representative; and
              \item up to four General Committee members.
          \end{enumerate}
\end{enumerate}


\section{Executive Positions}
Executive positions are defined in the Constitution, including information regarding each role's responsibilities and eligibility criteria.


\section{Office Bearing Positions}

\subsection{The Duck Lounge Liaison}
\begin{enumerate}[(1)]
    \item The Duck Lounge Liaison is responsible for the management of the Duck Lounge. They are responsible for the maintenance of the Duck Lounge, and for liaising with the School of Computer Science regarding the Duck Lounge.
    \item The Duck Lounge Liaison is responsible for:
          \begin{enumerate}[(a)]
              \item the management of the Duck Lounge; and
              \item the maintenance of the Duck Lounge; and
              \item liaising with the School of Computer Science regarding the Duck Lounge; and
              \item making recommendations to the Committee regarding facilities in the Duck Lounge, including but not limited to furniture, equipment, and decorations.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Duck Lounge Liaison.
\end{enumerate}

\subsection{Business Manager}
\begin{enumerate}[(1)]
    \item The Business Manager is responsible for the management of the Club's business operations. They are responsible for the maintenance and procurement of stock.
    \item The Business Manager is responsible for:
          \begin{enumerate}[(a)]
              \item the management of the Club's business operations; and
              \item the maintenance and procurement of stock; and
              \item making recommendations to the Committee regarding the Club's business operations; and
              \item setting the prices of stock; and
              \item working with the Treasurer to ensure that the Club's business operations are financially viable.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Business Manager.
\end{enumerate}

\subsection{Partnerships \& Sponsorships Officer}
\begin{enumerate}[(1)]
    \item The Partnerships \& Sponsorships Officer is responsible for assisting the Partnerships \& Sponsorships Manager in their tasks.
    \item The Partnerships \& Sponsorships Officer is responsible for:
          \begin{enumerate}[(a)]
              \item assisting the Partnerships \& Sponsorships Manager in managing the Club's partnerships and sponsorships; and
              \item the establishment of new partnerships and sponsorships; and
              \item the maintenance of existing partnerships and sponsorships.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Partnerships \& Sponsorships Officer.
\end{enumerate}

\subsection{Graphic Designer}
\begin{enumerate}[(1)]
    \item The Graphic Designer is responsible for creating the graphics for the Club for use in areas including but not limited to events and marketing.
    \item The Graphic Designer is responsible for:
          \begin{enumerate}[(a)]
              \item creating graphics for the Club, including but not limited to posters, banners, logos, and other graphics as required by the committee; and
              \item ensuring that the material created for the Club is consistent with the brand identity and goals of the committee and the Club as a whole; and
              \item assisting the Social Media \& Marketing Officer(s) by creating graphics and other promotional material, where required.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Graphic Designer.
\end{enumerate}

\subsection{Social Media \& Marketing Officer}
\begin{enumerate}[(1)]
    \item The Social Media \& Marketing Officer is responsible for the management of the Club's social media accounts, and for the marketing of the Club.
    \item The Social Media \& Marketing Manager is responsible for:
          \begin{enumerate}[(a)]
              \item the management of the Club's social media accounts; and
              \item the marketing of the Club; and
              \item the promotion of Club activities and events; and
              \item the promotion of information from our sponsors and partners.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Social Media \& Marketing Officer.
\end{enumerate}

\subsection{Open Source Officer}
\begin{enumerate}[(1)]
    \item The Open Source Officer is responsible for the management of the Club's open source initiatives and leading the Open Source Team of the Club. The Open Source Team is a largely self-sufficient body with oversight by the committee on major changes. The team is free to receive support from any willing volunteers.
    \item The Open Source Officer is responsible for:
          \begin{enumerate}[(a)]
              \item maintaining the Club's open source projects, including but not limited to:
                    \begin{enumerate}[(i)]
                        \item overseeing projects on GitHub or any other code-sharing platforms; and
                        \item assigning issues, reviewing pull requests, performing code reviews, and other required tasks; and
                    \end{enumerate}
              \item onboarding club members and volunteers to work on the Club's projects; and
              \item proposing new projects and setting them up; and
              \item leading the Open Source Team.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Open Source Officer.
\end{enumerate}

\subsection{Equity Officer}
\begin{enumerate}[(1)]
    \item The Equity Officer is responsible for the management of the Club's equity initiatives. They are responsible for ensuring Club events are accessible to all members of the Club, and for ensuring that the Club is a safe and inclusive environment for all members.
    \item The Equity Officer is responsible for:
          \begin{enumerate}[(a)]
              \item the management of the Club's equity initiatives; and
              \item ensuring Club events are accessible to all members of the Club; and
              \item ensuring that the Club is a safe and inclusive environment for all members of the Club; and
              \item being available to hear concerns from members regarding the club and/or its members and taking responsible action; and
              \item making recommendations to the Committee regarding diversity and inclusion in the Club.
          \end{enumerate}
    \item All members of the Club are eligible to nominate for Equity Officer.
\end{enumerate}


\subsection{First-Year Representative}
\begin{enumerate}[(1)]
    \item The First-Year Representative is responsible for representing the interests of first-year students in the Club. They are responsible for ensuring that first-year students are aware of the Club's events and initiatives, and for ensuring that the Club's events and initiatives are accessible to first-year students.
    \item The First-Year Representative is responsible for:
          \begin{enumerate}[(a)]
              \item representing the interests of first-year students in the Club; and
              \item ensuring that first-year students are aware of the Club's events and initiatives; and
              \item ensuring that the Club's events and initiatives are accessible to first-year students; and
              \item making recommendations to the Committee regarding first-year students in the Club.
          \end{enumerate}
    \item To be eligible for the position, the nominee must be:
          \begin{enumerate}[(a)]
              \item a first-year student of the University of Adelaide; and
              \item a member of the club.
          \end{enumerate}
    \item The position is elected at the SGM in Semester 1 each year, rather than the AGM.
\end{enumerate}

\section{Committee Positions}

\subsection{General Committee}
\begin{enumerate}[(1)]
    \item General Committee members are responsible for assisting the Executive and Office Bearers in the management of the Club.
    \item All members of the Club are eligible to nominate for General Committee.
\end{enumerate}

\subsection{Responsibilities of all Members of the Committee}
All members of the Committee have a responsibility to:
\begin{enumerate}[(a)]
    \item attend all meetings of the Committee, and General Meetings; and
    \item act in the best interests of the Club; and
    \item act in accordance with the Constitution and this Schedule; and
    \item act in accordance with the Clubs Policy of YouX.
\end{enumerate}

\subsection{Number of Positions}
The number of positions in the Committee may be limited by the Executive at their discretion. The Executive may limit the number of positions in the Committee to a number less than the number of nominations received. The current composition of the Committee as approved by the Executive is listed in \Cref{appendix:tablePositions}.

\appendix
\section{Table of Positions and Their Number of Offices}\label{appendix:tablePositions}
\begin{center}
    \vspace{1em}
    \def\arraystretch{1.1}
    \begin{tabular}{c|c}
        \textbf{Position}                    & \textbf{Amount} \\
        \hline
        President                            & 1               \\
        Vice-President                       & 1               \\
        Treasurer                            & 1               \\
        Secretary                            & 1               \\
        Partnerships \& Sponsorships Manager & 1               \\
        Duck Lounge Liaison                  & 1               \\
        Business Manager                     & 1               \\
        Partnerships \& Sponsorships Officer & 2               \\
        Social Media \& Marketing Manager    & 1               \\
        Graphic Designer                     & 2               \\
        Social Media \& Marketing Officer    & 2               \\
        Open Source Officer                  & 2               \\
        Equity Officer                       & 1               \\
        First-Year Representative            & 1               \\
        General Committee                    & 4               \\
        \hline
        \textbf{Total}                       & \textbf{22}
    \end{tabular}
\end{center}

\newpage
\input{endorsement}

\end{document}
